Jug: Software for Reproducible Computation

### 2012-01-23 paper.tex
TEX Add bibliography
STYL Make it narrower

\hypersetup{%
    bookmarks=true,
    colorlinks=true,
    pdfauthor={Luis Pedro Coelho},
    citecolor=pondgreen,
    urlcolor=toastedchilipowder,
    linkcolor=toastedchilipowder,
}
\let\code\texttt

@@

In [2]: value(counts)
Out[2]: [7, 7, 7, 7, 7, 7, 7, 7, 7, 7, 8, 8, 8, 8, 8, 8, 8, 8, 8, 8]
\end{verbatim}
\end{center}
\caption{Interaction with \code{jug shell}.}
\label{fig:jug-shell-interaction}
\end{figure}

@@

# pyslic.computefeatures takes an image and an identifier of the feature set
# and returns a set of features (as a numeric array).
#
# TaskGenerator can be used directly to adapt existing functions
computefeatures = TaskGenerator(pyslic.computefeatures)

@@

\end{document}

>>>>

\hypersetup{%
    bookmarks=true,
    colorlinks=true,
    pdfauthor={Luis Pedro Coelho},
    citecolor=pondgreen,
    urlcolor=toastedchilipowder,
    linkcolor=toastedchilipowder,
}
\let\code\texttt
\addbibresource{references.bib}

@@

In [2]: value(counts)
Out[2]: [7, 7, 7, 7, 7, ... 8, 8, 8, 8, 8, 8, 8, 8, 8]
\end{verbatim}
\end{center}
\caption{Interaction with \code{jug shell}. The \code{value} function loads and
returns the result from any task. The final line has been edited (marked with
\ldots) for presentation purposes.}
\label{fig:jug-shell-interaction}
\end{figure}

@@

# pyslic.computefeatures takes an image and an identifier of the
# feature set and returns a set of features (as a numeric array).
#
# TaskGenerator can be used directly to adapt existing functions
computefeatures = TaskGenerator(pyslic.computefeatures)

@@

\printbibliography
\end{document}
